Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-25 bbbq_article.tex
Process feedback
Macrh 25th

The first query was a call to the 'gene' database for the 
term 'membrane protein' (in all fields) for the organism \textbf{Homo sapiens}.
This resulted in 1077 gene IDs
[RJCB:
  This was December 2020.
  At 2021-03-01, one will get 1130 gene IDs.
  Also, one of the gene IDs that was valid back then,
  has been obsoleted.
].
The next query was a call to the 'gene' database 
to obtain the gene names from the gene IDs.
Per gene name, the 'dbSNP' NCBI database is queried for 
variations associated with the gene name.

@@

We next wondered if this over-representation would also generalize to MHC-II. 
Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc2}) 
for the TMH and epitope counts.
We show that MHC-II has the same pattern of over-presentation
as MHC-I, yet this over-presentation is more pronounced. 
\frans{
  we should explain this does it like shown for mhc-I also 
  linearly correlates with the hydrophopbicity 
  of the MHC-II binding cleft?
}
Also for MHC-II, we observe that the extent to which TMH-derived
epitopes are presented is similar between the haplotypes, for
a human, bacterial and viral proteome.

@@

The over-presentation of TMHs for MHC-II haplotypes 
is more pronounced than for MHC-I,
as with a third of the predicted binders 
HIERO
from the human and MtB proteome stem from TMH human reference proteome and MtB reference proteome to be presented on MHC-II. \frans{ik zoek nog naar associaties}

such as \verb;HLA-DQA1*0101/DQB1*0501;

>>>>

The first query was a call to the 'gene' database for the 
term 'membrane protein' (in all fields) for the organism \textbf{Homo sapiens}.
This resulted in 1077 gene IDs
% 1077 gene IDs is correct for December 2020.
% At 2021-03-01, one will get 1130 gene IDs.
% Also, one of the gene IDs that was valid back then,
% has been obsoleted.
The next query was a call to the 'gene' database 
to obtain the gene names from the gene IDs.
Per gene name, the 'dbSNP' NCBI database is queried for 
variations associated with the gene name.

@@

We next wondered if this over-representation would also generalize to MHC-II. 
Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc2}) 
for the TMH and epitope counts.
We show that MHC-II has the same pattern of over-presentation
as MHC-I, yet this over-presentation is more pronounced. 
\richel{
  Showing how general our finding is (as it is explained by hydrophobicity)
  is important. See \url{https://github.com/richelbilderbeek/bbbq_article/issues/192}
}
Also for MHC-II, we observe that the extent to which TMH-derived
epitopes are presented is similar between the haplotypes, for
a human, bacterial and viral proteome.

@@

The over-presentation of TMHs for MHC-II haplotypes 
is more pronounced than for MHC-I,
as with a third of the predicted binders 
\richel{Hier ben ik nu met verwerken...}
from the human and MtB proteome stem from TMH human reference proteome and MtB reference proteome to be presented on MHC-II. \frans{ik zoek nog naar associaties} 
such as \verb;HLA-DQA1*0101/DQB1*0501;
